An Overview of the Current State of Test-First vs. Test-Last Debate

### 2013-11-26 Paper_Draft.tex
Final Draft for monday.

\keywords{ACM proceedings, \LaTeX, text tagging}

@@

The paper is divided into five sections.  In Section II we discuss what software testing is and current software development models with their supporting testing methods: test-first and test-last testing.  In Section III we will provide an analysis of the data explaining the potential advantages and disadvantages of test-first testing compared to test-last testing.  In Section IV we discuss issues of using test driven development to implement test-first testing. In Section V we will go over new testing methodologies based on test-first development. In Section VI we will provide conclusions and suggestions for further research in the field.

@@

Due to the changes in Agile programming, test-last testing was pushed aside in favor of a different style known as test-first testing.  In 2001, with the release of the agile development prachttp://start.fedoraproject.org/tice Extreme Programming, the idea of test-first testing, implemented in test driven development, started to become popular for the first time ~\cite{Hammond:2012}. Test-first testing is the practice of writing tests before code has been written and then writing code to make the tests pass.  It should be noted that since tests are written before production code, test-first testing tends to be heavily linked to development methods and thus the most common test-first models also include development elements as well.

@@

\subsection{Understanding Contradictions}
Many summaries of TDD research ~\cite{Hammond:2012, Hellman:2012, Kettunen:2010, Kollanus:2010} have noted that studies that compare test-first to test-last testing tend to contradict one another.  Kollanus points out that articles in her review contradicted other articles which made it hard to make sound conclusions from the research given, especially on the subject of productivity.  The amount of contradictions concerned Kollanus enough that she noted the amount of contradictions as a potential confounding factor for her results.  Contradictions also existed between our review by Kollanus and our experiment by Lemos et al.  Although both articles seem to agree that code coverage is increased with test-first methods neither study seems to totally agree on the attributes of code correctness or total development time.  Since contradictions occur often in the results of our study we considered it to be important to explore some current theories on why these contradictions exist.  In particular we will be exploring two potential causes: participant experience and improper study implementation/ documentation.

In the case of participant experience there seems to be a skill gap between test first and test last testing.  This gap is best shown by the results from Janzen  Coding professionals, on the other hand, actually preferred test first programming and were much more comfortable with it than students.  They also stated they felt it was relatively easy to understand while students did not. In another opinion study ~\cite{Kettunen:2010}, by Kettunen et al, a common theme throughout the paper was examples of individual testimonies and research conclusions that pointed to test first testing being harder to implement than test last testing.   Considering that most conducted experiments focus on college students and industry professionals, who have vast experience differences, the fact that test first testing may be harder to implement for college students compared to industry professionals may create differing results between studies.   This idea is considered in ~\cite{Hammond:2012} and ~\cite{Kettunen:2010}, but no summary papers where found considering this result and comparing student participant experiment results to professional participant experiment results.

The other problem that has plagued summary papers of test first testing is that most studies either lack documentation in key locations or do not effectively handle the participant conformance issue which comes up in TDD studies.  In the literary review by Kollanus, she acknowledges a frustrating lack of information in many studies on how TDD was implemented.  Most studies, claimed Kollanus, had maybe one or two lines describing their TDD methodology or just simply claimed that they used TDD.  Considering that TDD can be implemented in many ways, as discussed earlier in the background, Kollanus states that the lack of documentation for TDD implementation means that, as a reviewer, she has no idea if the test methods used to produce the results were similar or different, potentially confounding some of her conclusions.  Another issue similar to this is the conformance issue, brought up in (cite here).  The conformance issue in TDD testing refers to the fact that few researchers make sure that TDD was implemented correctly or at all by its participants.  For example, in the study by Lemos et. al the researchers acknowledged that one of their confounding factors was that they only asked students to write tests before code, thus a variety of different test first methods might have been used within the study making its data less conclusive.   Overall the lack of documentation of how researchers specifically planned to implement TDD in their study and their lack of some sort of monitoring of whether the implementation was actually occurring greatly reduces the credibility of the research being done and allows for confounding factors to potentially occur.

@@

Due to current issues in contradictory data it is hard to make solid conclusions about the advantages and disadvantages of using test first testing instead of test last testing.  What can be done instead is we can consider certain trends in research that can suggest potential answers.  Most studies and summaries seem to agree that test-first testing tends to produce more test coverage compared to test-last testing and that test first testing tends to take longer to write tests compared to test first testing.  Two of the studies we looked at, the experiment by lemos and the literary review by Kollanus, point out these two trends.  Also one or both trends have been noted through multiple papers ~\cite{Kettunen:2010, Hammond:2012, Hellman:2012} with no major contradictions found.  Another convincing trend that has occurred is that in general test first testing seems to be harder to implement than test last testing as mentioned earlier.   Although these trends seem to be clear, the rest seem to be more muddled.  Code correctness for example seems to have no clear trend as multiple studies have reached contradictory conclusions to other studies.  Another hot button topic that fails to show a trend one way or the other is the amount of time spent simply developing code as this again seems to have results across the board.  From these trends we can consider that test first testing overall probably takes more time to write, increases code coverage, and is harder to implement than test-last testing and that other advantages or detriments may exist but they are unclear in current research.

\section{Test Driven Development}
\mycomment{newly added section, still rough at best}

Test-first testing in most of these studies are being done in various forms of TDD.  Because of this, the data for test-first testing has the potential to reflect traits of TDD which are independent of any traits in test-first testing.  Although all the results have a potential to contain this issue one particular result seems to suggest it may be a trait of TDD, not test-first testing.  This trait is that Test-first testing is more difficult then test last testing.

\subsection{Studies noting TDD difficulty}
Hammond et. al states in his research summary paper on TDD that: "TDD remains deceptively simple to describe but deeply challenging to put into practice effectively" `\cite{Hammond:2012}.  Hammond reaches this conclusion with the use of multiple studies that show implecations that TDD is complex.  Some of the studies used to draw this conclusion are summarized below.

In the study by Janzen 2007, there was an interesting relation between two different measurement aspects of the opinion study.  It was noted by Janzen that in every experiment, slightly less people said they would be more likely to implement TDD than people who said that TDD was a superior method to test-last methods. This means that more people thought that TDD was the better method to implement than  people who said they would actually implement TDD.  Janzen attributed this phenomena as a testament to the difficulty of TDD as he found in the comments section multiple survey participants mentioned that they felt that TDD was too difficult or too different from what they normally do.

In a study done by George and Williams,  \mycomment{cite this article!} multiple programming professionals from John Deere, RoleModel Software, and Ericsson participated in an experiment comparing TDD to waterfall development.  In this study a 9 question survey was given out asking programmers what they thought about TDD and what was difficult with TDD.  In this survey 56\% of the professionals noted that they had difficulty adapting to the TDD mindset when participating the study.  In addition 23\% of the participants noted that they felt that the lack of upfront design in TDD was more of a hindrance then a help.

In an online survey done by Aniche and Gerosa ~\cite{Aniche:2010}, 218 TDD programmers of differing skill levels were surveyed about their TDD practices and mistakes.  In the survey it was found that TDD was not easy to follow as about 25\% of the programmers admitted to frequently or always making mistakes in following the traditional steps of TDD.  Two examples of these mistakes include: forgetting to clean up their code after a test passes and writing tests that are too complex for effective TDD.

\subsection{Reasons for TDD Difficulty}
The data above shows fairly strong evidence that TDD is at least somewhat difficult to implement but none of the data above shows that test-first testing is the problem.  In the first study, Janzen reveals that TDD was difficult for some people to implement.  In the second study, George and Williams reveal that 56\% of the participants found the TDD mindset hard to adapt while only 23\% of the participants found testing before designing as a problem, suggesting that something other then test-first testing caused difficulty for at least 33\% of the participants.  Whereas the third study shows that programmers have some trouble implementing the steps of TDD, which has nothing to do with testing before designing.  Since difficulty in using TDD does not seem to be directly linked with test-first testing, that suggests that there is different issue causing TDD to be difficult to implement.

One potential issue with TDD that is brought up by many developers is that it fails to explain the best way to implement tests to test your codes wanted functionality.  This is best represented in a quote from Dan North's article \mycomment{cite Introducing BDD here}: "While using and teaching agile practices like test-driven development (TDD) on projects in different environments, I kept coming across the same confusion and misunderstandings. Programmers wanted to know where to start, what to test and what not to test, how much to test in one go, what to call their tests, and how to understand why a test fails."  This issue as shown in Dan North's article may reveal why TDD is so difficult.  If the issue for why TDD is so difficult is similar to something like the issue explained above then perhaps they may be a better implementation other than TDD that exists.

\section{evolutions to TDD}
\mycomment{this section is currently a work in progress}

As can been seen in the above section there is an issue where TDD can be difficult to implement correctly.  Due to this issue, new methods are starting to appear in the agile community that contain some of TDD's main tenets but have shifted enough away from TDD at some fundamental level that they are starting to receive their own names and classifications.  Although there are many of TDD spin-offs, for this paper we chose to focus on two more popular spin offs, acceptance test driven development and behavior driven development.
http://start.fedoraproject.org/
\mycomment{add lack of research disclaimer}

\subsection{Acceptance Test Driven Development}

Perhaps the closest spin off to TDD, acceptance test driven development (ATDD), follows many of the ideas and expectations that regular TDD does, like writing tests first and using tests to define the development code.  Unlike TDD, though, ATDD believes that in order to produce higher quality code, reduce coding confusion, and promote better customer satisfaction, customers should write or define "acceptance" tests.  These acceptance tests are tests that are required to pass before the customer will accept the product and usually define the core functionality of the product being developed.  This part of ATDD is noticeably different from the TDD ideology because in the TDD ideology only the developer should writes the tests and the tests should be written from simplest to hardest.~\cite{Hammond:2012}

The shift from having the developer write all the tests to the customer having to write some of tests is ideally considered a win win.  The shift of the workload of determining main functionality from the developer to the customer significantly reduces the difficulty of the TDD practice to the developer as they are no longer concerned about writing and determining all the functionality for their code.  This method is also supposed to benefit the customer as it allows the customer to get the product they desire.  One of the major complaints of ATDD is that it is an ideal practice at best because customers will not take the time to create useful acceptance tests.~\cite{Hammond:2012} Another complaint of ATDD is that its very hard for  customers to write useful acceptance tests  because they view functionality differently then developers because their knowledge of code is limited.(site new IEEE article here)  Because of these varied complaints, some of the promoters of ATDD have moved away from it to support a newer similar TDD spin off, Behavior Driven Development.

\subsection{Behavior Driven Development}
\mycomment{somewhat stubbed section atm}
Behavior Driven Development, or BDD, is a new spin off of TDD that focuses on how to correctly implement the fundamental usefulness of TDD.  The main difference between BDD and TDD is that TDD focuses on "testing the code" while BDD focuses more on defining a codes behavior. 
In order to do this, BDD focuses on defining a codes wanted functionality in plain English and then converts that plain English into tests using various programming tools and methods \mycomment{cite dan North and hammond article here}. This differs from TDD, because in TDD, their is no focus on defining code functionality in terms of plain English or even focusing specifically on code functionality.

The argued pros for BDD is that it can bypass many of the difficulties of TDD by allowing us to define the purpose of our code in more natural terms. This style removes much of the confusion about what is important to test in TDD and the other pro is that now it is easier to communicate goals and functionality of the code to non computer science majors (IE Managers, Customers, Sales Reps, etc.) which allows for higher customer satisfaction.

\section{conclusion}
\mycomment{this section is currently a work in progress}
\subsection{Conclusion intro}

In this paper we talked about two common test methods: test-first testing, often found in waterfall development models and test-last testing, often found in agile development models.  In section two we defined these test methods as well as provided background information to the reader.  In section three we explored recent research into the comparison of the two different testing methods and explored potential research problems with the current data.  In particular we found that data was contradictory but we still were able to tentatively conclude that test-first testing increases test coverage, increases time taken to test, and is harder to implement than test-last testing.  In this section we also suggested two potential reasons for the contradictory data: different participant experience levels and poor documentation/implementation of specific test first methods. In section four we explored different implementations of test first testing.

\subsection{Discussi or BDDon of Implications of Section 3}
\mycomment{stubbed for now}

\subsection{Discussion of Implications of Section 4}
\mycomment{stubbed for now}
\subsection{Suggestion for Further Research}
For people who are looking to advance the field of TDD it would be potentially very interesting to see how the new TDD spin-offs such as Behavior Driven Development and Agile Specification-Driven Development compare to that of a well documented TDD process like the one suggested for Extreme Programming.  Another useful study that could be implemented would be to compare the results of studies thing that could also help advance the field is to do research comparing the effectiveness of waterfall testing and TDD testing between groups with notably different experience levels as some research tentatively points that this may be a relevant variable.

\mycomment{This paragraph is a rough idea on the further research topic}

\mycomment{conclusion brain storm}

-TDD increases code test coverage

-TDD perhaps takes more skill to preform

-TDD may have more effective and less effective practices

-More study is needed.

-Better study methods should be implimented

>>>>

\keywords{Test Driven Development, Behavior Driven Development, Test-First, Test-Last, Agile, Waterfall, Testing, \LaTeX, text tagging}

@@

The paper is divided into four sections.  In Section II we discuss what software testing is and current software development models with their supporting testing methods: test-first and test-last testing.  In Section III we will provide an analysis of the data explaining the potential advantages and disadvantages of test-first testing compared to test-last testing.  In Section IV we discuss issues of using test driven development to implement test-first testing and will go over a new test-first methodology called behavior driven development. In Section V we will provide conclusions and suggestions for further research in the field.

@@

Due to the changes in Agile programming, test-last testing was pushed aside in favor of a different style known as test-first testing.  In 2001, with the release of the agile development practice Extreme Programming, the idea of test-first testing, implemented in test driven development, started to become popular for the first time ~\cite{Hammond:2012}. Test-first testing is the practice of writing tests before code has been written and then writing code to make the tests pass.  It should be noted that since tests are written before production code, test-first testing tends to be heavily linked to development methods and thus the most common test-first models also include development elements as well.

@@

\subsection{Understanding Contradictions}
Many summaries of TDD research ~\cite{Hammond:2012, Hellman:2012, Kettunen:2010, Kollanus:2010} have noted that studies that compare test-first to test-last testing tend to contradict one another.  Kollanus points out that articles in her review contradicted other articles which made it hard to make sound conclusions from the research given, especially on the subject of productivity.  The amount of contradictions concerned Kollanus enough that she noted the amount of contradictions as a potential confounding factor for her results.  Contradictions also existed between our review by Kollanus and our experiment by Lemos et al.  Although both articles seem to agree that code coverage is increased with test-first methods neither study seems to totally agree on the attributes of code correctness or total development time.  Since contradictions occur often in the results of our study we considered it to be important to explore some current theories on why these contradictions exist.  In particular we will be exploring two potential causes: method difficulty and improper study implementation/ documentation.

Method difficulty is considered a potential confounding factor when comparing test-first and test-last testing ~\cite{Hammond:2012, Kettunen:2010}. In particular, there is concern that test-first testing may be more difficult for beginning coders than test-last testing.  This is a concern because most study data comes from two sources with very different skill levels: industry professionals and college students.  In the study by Janzen et al, figures 1 and 2 show very different results between beginning and mature programmers.  In particular, beginner programmers did not report a very positive experience with test-first testing compared mature programmers.  This suggests that beginning coders may not be getting all the benefits from test-first methods that the more mature coders received.  If this is the case, then any summary method with mixed results between beginning and advanced programmers has a potential to have contradictory results.

The other problem that has plagued summary papers of test first testing is the lack documentation  and conformance of TDD methods in studies.  Kollanus, in her review paper, acknowledges a frustrating lack of information in many studies on how TDD was implemented.  Most articles, claimed Kollanus, had perhaps one or two lines describing their TDD methodology or only claimed that they used TDD.  Considering that TDD can be implemented in many ways, this lack of documentation for TDD implementation creates a problem in accurately comparing two studies.  This is an issue because multiple TDD methods may not preform equally, causing potentially contradicting results.  This problem could be avoided if studies documented their TDD process.  Another problem with TDD studies is that very few confirm their participants correctly implemented TDD~\cite{Hammond:2012}.  For example, in the study by Lemos et. al, the researchers acknowledged that one of their confounding factors was that they only asked students to write tests before code, thus a variety of different test-first methods might have been used within the study making its data less conclusive.   Overall the lack of documentation of how researchers specifically planned to implement TDD in their study and their lack of some sort of monitoring of whether the implementation was actually occurring greatly reduces the credibility of the experiment being done and allows for contradictory results to occur.

@@

Due to current issues in contradictory data it is hard to make solid conclusions about the advantages and disadvantages of using test-first testing instead of test-last testing.  That being said current trends exist within the research that allow us to guess some of the traits of test-first methods compared to test-last methods.  One result which was very clear in the research was that of code coverage.  The results from Lemos et al and Kollanus suggest that test-first testing tends to produce more code coverage compared to test-last testing. This seems to be a fairly uncontested conclusion as~\cite{Kettunen:2010, Hammond:2012} reached the same conclusion and no contradictions were found in other articles.  Another convincing trend that has occurred is that test-first testing seems to be harder to implement than test-last testing.  This trend is apparent from the results in Janzen and also from studies~\cite{Aniche:2010, George:2003} which will be discussed in the next section.     Although these trends seem to be clear, the rest seem to be more muddled.  Code correctness, for example, seems to have only a vague trend that agrees that test-first methods do not have worse code quality then test-last methods.  The debate about whether or not test-first testing produces better code correctness though has yet to be resolved due to conflicting data.  Another muddled trend is that of total development time.  Currently, the only thing that can be concluded on this topic is that test-first likely takes at least as much time as test-last methods to implement though it is unclear if test-first take significantly longer then test-last methods.

\section{Difficulty and TDD}
Due to TDD's popularity, almost all test first testing studies are done using TDD.  Because of this, the data for test-first testing has the potential to reflect an attribute of TDD that is not an attribute of test-first testing.  Although all the results found in the previous section have the potential to contain this issue, one particular result seems to suggest it may be a attribute of TDD and not test-first testing.  This attribute is the difficulty of test-first testing.

\subsection{Studies noting TDD difficulty}
In 2012 Hammond et al did a summary paper on the current state of TDD.  In this paper Hammond et al states that: ``TDD remains deceptively simple to describe but deeply challenging to put into practice effectively"~\cite{Hammond:2012}.  Hammond et al defended their claim by summarizing several studies briefly that showed  the complexity of TDD.  In this section we will take a more in depth look at some of the studies Hammond et al used to draw their conclusion.  We will then in the next section discuss why these studies prove that the complexity is caused by the design of TDD and not test-first testing.

One of the studies that Hammond et al summarizes is the opinion study by Janzen.  In particular Hammond focuses on a quote from Janzens study: ``A few of the participants of the studies found TDD either too difficult or too different from what they normally do''.  This quote refers to an interesting relation found between the choice and best approach category.  It was noted by Janzen that in every experiment, there were more people who thought test-first was the best approach than people who would choose to implement test-first testing.  When Janzen looked into why this phenomena had occurred he found multiple statements in the comment section that claimed the difficulties of TDD and attributed the phenomena to TDD difficulty.

Another study that Hammond summarizes is a experiment survey by George and Williams~\cite{George:2003}.  In the study, multiple programming professionals from John Deere, RoleModel Software, and Ericsson participated in an experiment comparing TDD to waterfall development.  In this study a 9 question survey was given out asking programmers what they thought about TDD and what was difficult with TDD.  In this survey 56\% of the professionals noted that they had difficulty adapting to the TDD mindset when participating the study.  In addition 23\% of the participants noted that they felt that the lack of upfront design in TDD was more of a hindrance then a help.

The last study Hammond summarizes in this portion of the paper is an online survey done by Aniche and Gerosa~\cite{Aniche:2010}.  In the survey, 218 TDD programmers of differing skill levels were surveyed about their TDD practices and mistakes.  In the survey, it was found that TDD was not easy to follow as about 25\% of the programmers admitted to frequently or always making mistakes in following the traditional steps of TDD.  Two examples of these mistakes include: forgetting to clean up their code after a test passes and writing tests that are too complex for effective TDD.

\subsection{Discussion}
The data above shows fairly strong evidence that TDD is at least somewhat difficult to implement but none of the data above shows that test-first testing is the problem.  In the first study, Janzen reveals that TDD was difficult for some people to implement.  In the second study, George and Williams reveal that 56\% of the participants found the TDD mindset hard to adapt while only 23\% of the participants found testing before designing as a problem, suggesting that something other then test-first testing caused difficulty for at least 33\% of the participants.  The third study showed that programmers had trouble implementing the steps of TDD, which has nothing to do with testing before designing.  With these studies in mind, difficulty in using TDD does not seem to be directly linked with test-first testing.  This suggests that a different issue is causing TDD to be difficult to implement.

One potential issue with TDD that is brought up by many developers is that it fails to explain how to write good test-first tests.  This is best represented in a quote from Dan North's article~\cite{North:xxx}: ``While using and teaching agile practices like test-driven development (TDD) on projects in different environments, I kept coming across the same confusions and misunderstandings. Programmers wanted to know where to start, what to test and what not to test, how much to test in one go, what to call their tests, and how to understand why a test fails."  In this quote Dan North expresses his and other coders frustration with TDD and its failure to specify how and what tests should be written.  This problem is also mentioned in articles~\cite{Kettunen:2010, Seoken:2012}.  Currently their is no empirical evidence that this could be the cause of the TDD difficulty, but it is currently suspect by knowledgeable experts in the field.

\section{Evolutions of TDD}

New test-first methods are starting to appear in the agile community that contain some of TDD's main tenets but are different enough from TDD that they are starting to receive their own names and classifications.  These new methods are starting to appear because many developers in one or another are not satisfied with the current implementation of TDD.  In this subsection we will discuss one of these popular TDD spin-offs, behavior driven development, which was developed to combat the problem noted in the previous paragraph.

%\subsection{Acceptance Test Driven Development}

%Perhaps the closest spin off to TDD, acceptance test driven development (ATDD), follows many of the ideas and expectations that regular TDD does, like writing tests first and using tests to define the development code.  Unlike TDD, though, ATDD believes that in order to produce higher quality code and reduce code, customers should write or define "acceptance" tests.  These acceptance tests are tests that are required to pass before the customer will accept the product and usually define the core functionality of the product being developed.  This part of ATDD is noticeably different from the TDD ideology because in the TDD ideology only the developer should writes the tests and the tests should be written from simplest to hardest.~\cite{Hammond:2012}

%The shift from having the developer write all the tests to the customer having to write some of tests is ideally considered a win win.  The shift of the workload of determining main functionality from the developer to the customer significantly reduces the difficulty of the TDD practice to the developer as they are no longer concerned about writing and determining all the functionality for their code.  This method is also supposed to benefit the customer as it allows the customer to get the product they desire.  One of the major complaints of ATDD is that it is an ideal practice at best because customers will not take the time to create useful acceptance tests.~\cite{Hammond:2012} Another complaint of ATDD is that its very hard for  customers to write useful acceptance tests  because they view functionality differently then developers because their knowledge of code is limited.(site new IEEE article here)  Because of these varied complaints, some of the promoters of ATDD have moved away from it to support a newer similar TDD spin off, Behavior Driven Development.

Behavior Driven Development, or BDD for short, was created by Dan North as a substitution for TDD that helps the user determine what to test and how to test it.  The main difference between BDD and TDD is that TDD focuses on testing the code itself while BDD focuses more on testing a codes intended behavior. In order to do this, BDD users start by considering their codes intended functionality.  They then sentences that use their native language to define what they want their code to achieve.  These sentences are then converted from the programmers native language to tests in a standard testing language using various programming tools and methods that have been developed specifically for BDD \cite{Soeken:2012, North:xxx, Hammond:2012}. This differs from TDD because the focus is no longer on testing new features but on defining what these new features should do.  This shift in focus and use of native language to define problems, according the Dan North, is what makes BDD simpler to implement. \cite{North:xxx}

\section{conclusion}
\subsection{Summary}

In this paper we talked about and compared two common test methods: test-first testing and test-last testing.  Within this discussion we reviewed current research in the field in an attempt to make conclusions about the advantages and disadvantages of test-first and test-last methods.  In this part of the paper we were somewhat able to conclude that test-first testing increases code coverage, is more difficult to implement, has at least as much code correctness, and takes at least as long to develop as test-last testing.  These conclusions must be considered weak though as we noted that studies were very contradictory to one another due to various factors including method difficulty and poor study design/documentation.  We also discussed how there seems to be evidence that being harder to implement is not a problem with test-first testing but with TDD, the way test first testing is usually implemented.  We ended by exploring a new test-first method that had the potential to fix this issue with TDD.

\subsection{Suggested Further Research}
For people who are looking to increase clarity in the debate between test-first and test-last testing there are a few studies that would be quite useful in its current state.  One helpful study that could be implemented is a summary study of TDD and test-first testing articles which are divided up by participant coding expertise to see if participants with different programing experience achieve differing results.  Another useful study that could be implemented would be to compare the new BDD method against TDD to see if participants find BDD simpler to implement than TDD.  Also any new research on the debate that has a well documented TDD method and has some way to confirm that participants preformed this method would be useful in helping to solve the debate by giving it more creditable studies to work with.
